%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Embedded Design Engineer \& Security Expert (Team Lead)} % Job title
    {Europäische Funk-Rundsteuerung(EFR) GmbH} % Organization
    {Munich, Germany} % Location
    {Jun. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed BSI (Bundesamt für Sicherheit in der Informationstechnik) complient secured software architecture for SMGW (Smart Meter Gateway).}
        \item {Implemented secured Linux boot workflow for Atmel's SAM5D35 MCU (ARM cortex A5).}
        \item {Integrated smartcard with SMGW and ported crypto related functionalities to smartcard.}
        \item {Developed RESTful API client to communicate with energy management server.}
        \item {Making the SMGW CC(Common Criteria) compliant (ISO/IEC 15408).}
        \item {Tools :- Openssl, Buildroot, Wireshark, Eclipse, CMake, Doxygen etc.}
        \item {Protocol :- TLS/SSL 1.2, HTTP, ISO7816, NTP, SOCKSV5 etc.}
        \item {Platform :- Atmel's SAM5D35 (ARM cortex A5), Broadcom's BCM2837( ARM Cortex A53).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Digital Design and Research Engineer} % Job title
    {Department for Integrated Systems, TUM} % Organization
    {Munich, Germany} % Location
    {Dec. 2015 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ported the digital design from Chipit to ProFPGA hardware.}
        \item {Debugging the bugs in digital design of Network Adapter for InvasIC micro-architecture.}
        \item {Tools :-  Synplify Pro, Chipitpro, Chipscope, Modelsim and grmon.}
        \item {Protocol :- AHB-AMBA, APB-AMBA.}
        \item {Platform :- Chipit (Xilinx Vertex-5), ProFPGA (Xilinx Vertex-7).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Design Werkstudent} % Job title
    {Department for Real-Time Systems, TUM} % Organization
    {Munich, Germany} % Location
    {Aug. 2015 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed RSSI based local positioning system for BLE module NRF51822 using iBeacon.}
        \item {Integrated the developed module with existing modules on ARM cortex-M0+ of NRF51822.}
        \item {Tools :- GCC, Eclipse, Keil, NRF Studio, GDB etc.}
        \item {Protocol :- BLE 3.0 (Bluetooth Low Energy), iBeacon.}
        \item {Platform :- NRF51822 (ARM Cortex M0), iBeacon.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lab Tutor} % Job title
    {Department for Integrated Systems, TUM} % Organization
    {Munich, Germany} % Location
    {Apr. 2015 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lab tutor for HW-SW Co-design lab.}
        \item {Tools :- Vivado, ISE, Modelsim, GCC etc.}
        \item {Protocol :- Xillybus, AHB-AMBA, AXI-AMBA etc.}
        \item {Platform :- Xilinx Zynq-7000.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Digital Design Werkstudent} % Job title
    {Department for Integrated Systems, TUM} % Organization
    {Munich, Germany} % Location
    {Nov. 2014 - Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a new module for HW-SW Co-design lab and wrote the lab manual for the same.}
        \item {Developed a video processing accelerator on FPGA (Zynq-7000) and its software counterpart on ARM cortex-A9 processor.}
        \item {Tools :- Vivado, ISE, Modelsim, GCC etc.}
        \item {Protocol :- Xillybus, AHB-AMBA, AXI-AMBA etc.}
        \item {Platform :- Xilinx Zynq-7000.}
      \end{cvitems}
    }

%---------------------------------------------------------
    %---------------------------------------------------------
  \cventry
    {Wireless Research Werkstudent} % Job title
    {Siemens (Corporate Research)} % Organization
    {Munich, Germany} % Location
    {Jan. 2014 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and implemented algorithm for motion sensing using RSSI values of Wi-Fi communication.}
        \item {Worked on distance measurement using time of arrival of Wi-Fi packets.}
        \item {Evaluated communication power of Atmel's Wi-Fi module.}
        \item {Tools :- Matlab, Wireshark, Tshark, GCC etc.}
        \item {Protocol :- IEEE 802.11 n (WiFi).}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
