%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Ankit }{Kalbande}
\position{Embedded Linux Engineer{\enskip\cdotp\enskip}Security Expert}
\address{Helene-Mayer-Ring 7B/452, 80809 München, Germany}

\mobile{(+49) 176-55155443}
\email{ankitkalbande@gmail.com}
\homepage{}
\github{}
\linkedin{ankitkalbande}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Mr./Ms./Dr. LastName,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Claud D. Park~~~Â·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

%\lettersection{About Me}
I wish to present my candidature for the position of ’Embedded Systems Engineer -Automotive Systems’ at Intel, as the requirements for the position considerably matches with my profile.

I am currently working as a full time research scholar at Lehrstuhl fur Integrierte Systeme (LIS) in Technische Universitat Munchen (TUM) from past 4 months, I had completed my graduation in Communication Engineering at TUM with 1.6 grade. During my studies and jobs, I had acquired in-depth knowledge of digital
design and verification languages such as VHDL, Verilog and SystemC and scripting languages such as shell, TCL and perl. I had worked on wide range of EDA tools from Mentor Graphics(Modelsim), Xilinx(Vivado, ISE, Impact, Chipscope) and Synopsys(Synplify, Chipit Pro).

My experience includes developing a lab module for hardware software co-design lab at Lehrstuhl fur Integrierte Systeme TUM. In this lab module, I had developed a video processing accelerator on Zynq-7000 FPGA along with its Linux driver. I had also authored the lab manual and tutored the designed lab in following
semester. My experience also includes developing a cache coherency controller IP core for multi-tile Invasic architecture. The functionality of designed IP core was verified and prototyped on Chipit a multi-FPGA prototyping platform of Xilinx Virtex 5 FPGA.

Apart from SoC design, I am having experience of firmware development in Assembler, C and C++ with wide range of microcontroller like ATmega128, Atmega8, RX62T, ARM cortex A8, ARM cortex A9 and ARM cortex M0+. I had also worked on wide range of wired and wireless communication protocols like l2c, SPI, RS232, IEEE 802.11 (WIFI), IEEE 802.15.1 (Bluetooth) etc. While developing embedded applications, I had worked on multiple vendor specific tools like Arduino, Atmel Studio, Eclipse, Netbean, Keil, e2 studio etc.

I am a self-starter who can work with little or no supervision but I also possess excellent interpersonal skills with the ability to work as part of a group effectively. I would be very excited and highly grateful if I am given the opportunity to work at Intel. I am certain that I can make positive contributions to your ongoing projects and become a valuable member of your team if chosen for this job. I had attached my CV, which contains the details of my theoretical and practical training.

Eagerly waiting for your reply.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
